Work Fragmentation in Developer Interaction Data

### 2016-01-28 paper_2.tex
pass

Category \emph{refactoring} regroups usage of refactorings tools (rename, move methods, extract methods, etc). This is indicative of edition activities \RR{expand}

Category \emph{clean-build} regroup events related to build system usage (build the system, clean the build, run the build, the tests, etc). This is indicative of \RR{out of inspiration and time for now ...}

%- clear categories have clear outcome one way or the other
%- mixed categories have mixed outcomes
%=> overall pretty good then!

>>>>

Category \emph{refactoring} regroups usage of refactorings tools (rename, move methods, extract methods, etc). This is indicative of edition activities, rather than program comprehension. \RR{expand}

Category \emph{clean-build} regroup events related to build system usage (build the system, clean the build, run the build, the tests, etc). This is indicative of activities in which the programmer expects the program to be in a testable state. \RR{out of inspiration and time for now ...}

% -recall hypotheses
% - explain frequencies
% - present results
%- clear categories have clear outcome one way or the other
%- mixed categories have mixed outcomes
%=> overall pretty good then!
